---
title: "api-explorations"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    keep_md: true
    theme: lumen
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      out.width = "600px")

if (!require(tidyverse)) {
  install.packages("tidyverse")
}
```

## Purpose

This document explores the utility of using the Box.com API for file management.

## Set-up

The `boxr` package (https://github.com/r-box/boxr) provides the functionality we will be testing.

### Installing `boxr`

```{r}
if (!require("boxr")) {
  install.packages("boxr")
}
```

### Setting up Box for access by `boxr`

The instructions here--<https://r-box.github.io/boxr/>--are useful, especially those under the `Getting set up` section.

After creating the `PLAY-workflow` application, I entered the following code into an R console.

```{r}
boxr::box_auth()
```

After entering the credentials, I got a message that I am successfully logged in to Box.

## Testing `boxr` functions

### Creating a directory

Let's create a new directory to test the package's functions.

```{r}
play_dir_name <- "TEST-PLAY-workflow"
f <- boxr::box_dir_create(play_dir_name)
str(f)
```

That seemed to work.
We have stored the returned metadata in a variable `f`.
Now, let's create two subdirectories under that main directory.
First, we switch to the created directory and make it our temporary working directory.

```{r}
home_dir <- boxr::box_getwd()
boxr::box_setwd(f$id)
```

Then we create two directories, `qa`, and `data_collection`.

```{r}
qa <- boxr::box_dir_create("qa")
data_collection <- boxr::box_dir_create("data_collection")
```

### Listing created directories

Let's retrieve a list of directories in our current working directory.
The default is the current working directory.
Note: We need to load the `tidyverse` package to have access to the pipe `%>%` operator.

```{r}
play_dirs <- boxr::box_ls()

play_dirs %>% knitr::kable()
```

### Create a CSV data file and upload

Let's test the upload functionality by creating a CSV data frame and uploading it to one of the folders.

```{r}
df <- data.frame(name = c("Tom", "Dick", "Harriet"),
                 age = c(10, 15, 20),
                 alive = c(FALSE, TRUE, TRUE))
```

Let's create a Penn State `psu` and `nyu` subdirectory under `data_collection`.

```{r}
this_dir <- as.data.frame(play_dirs) %>%
  filter(name == "data_collection")
```

```{r}
psu <- boxr::box_dir_create(dir_name = "psu", parent_dir_id = this_dir$id)
nyu <- boxr::box_dir_create(dir_name = "nyu", parent_dir_id = this_dir$id)
nyu
```
Now that we have an `nyu` subdirectory, we can add a file to it.

For now, I'm going to have to export this file, then use saved file.

```{r}
readr::write_csv(df, "tmp.csv")
boxr::box_ul(nyu$id, file = "tmp.csv")
```

### Downloading uploaded file

Let's list the files in the `nyu` subdirectory first.

```{r}
nyu_list <- boxr::box_ls(nyu$id)
nyu_list
```

Now, we try to download it.

```{r}
boxr::box_dl(as.data.frame(nyu_list)$id, overwrite = FALSE, filename = "new_tmp.csv")
```

```{r}
downloaded_f <- readr::read_csv("new_tmp.csv")
str(downloaded_f)
```

Ok. That seems to work so far.

## Clean-up

For this workflow to be useful to others for testing, I need to delete the local temporary files.

```{r}
tmp_list <- list.files(pattern = "tmp.csv$")
lapply(tmp_list, file.remove)
```

I also need to delete the `TEST-PLAY-workflow` directory on Box.
That could be scripted, but for now, let's do that manually.
