---
title: "Session QA Prototyping Notebook"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: html_notebook
---

# Purpose

This document describes the process of prototyping and planning for the PLAY project session-level QA process based on files stored in Databrary.
The goal is to generate a session-specific report.

# Requirements

1. Given a Databrary volume, extract session info.
    - We will test with `https://nyu.databrary.org/volume/899`.
2. For each session, check the following:
    - Does the session folder name conform to the naming convention?
    - Is the sharing release level 'Authorized Users' or 'Learning Audiences'?
    - Are the following fields completed:
        - `birthdate`, `testdate`, `age`, `gender`, `race`, `ethnicity`, `language`, `disability`, `pilot`, `exclusion`, `group`, `setting`, `country`, `state`
    - Are there videos uploaded?
    - Do the videos conform to the file naming conventions?
    - Is the Natural Play video at least 1 hr long?
    - Is the Structured Play video at least X min long?
    
# Implementation steps

## Set-up details

```{r install-databraryapi}
if (!require(databraryapi)) {
  if (!require(devtools)) {
    install.packages("devtools")
  }
  devtools::install_github("PLAY-behaviorome/databraryapi")
}
```

```{r load-packages}
if (!require(tidyverse)) {
  install.packages("tidyverse")
}
library(tidyverse) # so we can use the '%>%' pipe operator
```

## Authenticate to Databrary

```{r}
databraryapi::login_db("rogilmore@psu.edu")
```

## Download spreadsheet for the test volume

```{r}
this_vol_id = 899

this_db_ss <- databraryapi::download_session_csv(vol_id = this_vol_id)

this_db_ss %>%
  knitr::kable(.)
```

## Session folder names follow naming convention

The session folder names should follow this format:

PLAY_\<SITE_CODE\>_\<SUB_ID\>-\<UNIQUE_CODE\>-\{HouseWalkthrough,NaturalPlay,StructuredPlay,DatabraryConsent,Questionnaires\}

Where \<SITE_CODE\> is one of the following:

```{r get-official-site-codes}
# Code to extract site codes from Google sheet


# Temporarily use a manual list of acceptable codes
site_codes <- c("NYU", "GTU", "PSU")
```

The \<SUB_ID\> is a 3 digit number that is equal to the`participant.ID` field from the spreadsheet.

The \<UNIQUE_CODE\> is generated according to the following algorithm:

**DESCRIBE ALGORITHM**

And the individual videos are labeled with one of the following labels: HouseWalkthrough, NaturalPlay, StructuredPlay, DatabraryConsent, Questionnaires.

### Functions to detect these elements

#### Session name format

```{r}
name_starts_with_PLAY_site_code <- function(session_nm, this_site_code) {
  stringr::str_detect(session_nm, paste0("PLAY_", this_site_code, "_"))
}

# This should fail
name_starts_with_PLAY_site_code(this_db_ss$session_name[1], "NYU")

# This should succeed
name_starts_with_PLAY_site_code(this_db_ss$session_name[12], "NYU")
```

```{r}
name_contains_sub_id <- function(session_nm, sub_id) {
  # Pad sub_id with leading zeros
  sub_id <- stringr::str_pad(sub_id, 3, pad = "0")
  stringr::str_detect(session_nm, sub_id)
}

name_contains_sub_id(this_db_ss$session_name[1], this_db_ss$participant.ID[1])

name_contains_sub_id(this_db_ss$session_name[12], this_db_ss$participant.ID[12])
```

```{r}
name_contains_site_sub_id <- function(session_nm, this_site_code, sub_id) {
  stringr::str_detect(session_nm, paste0("PLAY_", this_site_code, "_", stringr::str_pad(sub_id, 3, pad = "0"), "-"))
}

name_contains_site_sub_id(this_db_ss$session_name[12], "NYU", this_db_ss$participant.ID[12])
```

```{r}
name_contains_site_sub_id(this_db_ss$session_name[13], "NYU", this_db_ss$participant.ID[13])

name_contains_site_sub_id(this_db_ss$session_name[14], "NYU", this_db_ss$participant.ID[14])

name_contains_site_sub_id(this_db_ss$session_name[15], "NYU", this_db_ss$participant.ID[15])

name_contains_site_sub_id(this_db_ss$session_name[16], "NYU", this_db_ss$participant.ID[16])

name_contains_site_sub_id(this_db_ss$session_name[17], "NYU", this_db_ss$participant.ID[17])

name_contains_site_sub_id(this_db_ss$session_name[18], "NYU", this_db_ss$participant.ID[18])

name_contains_site_sub_id(this_db_ss$session_name[19], "NYU", this_db_ss$participant.ID[19])
```

Let's make this function more easily callable as an index into the session data frame.

```{r}
session_name_has_PLAY <- function(i, df) {
  first_four <- stringr::str_sub(df$session_name[i], 1, 4)
  stringr::str_detect(first_four, "PLAY")
}

session_name_has_site_id <- function(i, df, site_id) {
  site_id_from_name <- stringr::str_sub(df$session_name[i], 6, 8)
  site_id_from_name == site_id
}

session_name_has_sub_id <- function(i, df) {
  sub_id_from_name <- stringr::str_sub(df$session_name[i], 10, 12)
  sub_id_from_participant.id <- stringr::str_pad(df$participant.ID[i], 3, pad = "0")
  sub_id_from_name == sub_id_from_participant.id
}

session_name_has_correct_separators <- function(i, df) {
  has_first_underscore <- stringr::str_sub(df$session_name[i], 5, 5) == "_"
  has_second_underscore <- stringr::str_sub(df$session_name[i], 9, 9) == "_"
  has_first_dash <- stringr::str_sub(df$session_name[i], 13, 13) == "-"
    
  has_first_underscore && has_second_underscore && has_first_dash
}

session_name_play_id_valid <- function(i, df) {
  play_id <- stringr::str_sub(df$session_name[i], 14, 22)
  stringr::str_detect(play_id, "[:alnum:]+")
}

session_name_length_ok <- function(i, df, name_length = 23) {
  stringr::str_length(df$session_name[i]) == name_length
}

session_name_has_PLAY(12, this_db_ss)
session_name_has_site_id(12, this_db_ss, "NYU")
session_name_has_sub_id(12, this_db_ss)
session_name_has_correct_separators(12, this_db_ss)
session_name_play_id_valid(12, this_db_ss)
session_name_length_ok(12, this_db_ss)
```

Note that the `session_name_length_ok` fails because these names do not include a 23rd character.
In this case, ROG believes that is the initial 'S' in front of the subject ID.

```{r}
check_session_name <- function(i, df, site_id) {
  out_df <- dplyr::tibble(session_name = df$session_name[i],
                          name_has_PLAY = session_name_has_PLAY(i, df),
                          name_has_site_id = session_name_has_site_id(i, df, site_id),
                          name_has_sub_id = session_name_has_sub_id(i, df),
                          name_has_corr_seps = session_name_has_correct_separators(i, df),
                          name_play_id_valid = session_name_play_id_valid(i, df),
                          name_length_ok = session_name_length_ok(i, df))
  
  out_df
}

check_session_name(12, this_db_ss, "NYU")
check_session_name(13, this_db_ss, "NYU")
check_session_name(14, this_db_ss, "NYU")
```

```{r listify-check_session_name}
sess_checks_l <- lapply(12:14, check_session_name, this_db_ss, "NYU")
sess_checks <- Reduce(function(x,y) merge(x,y, all=TRUE), sess_checks_l)
sess_checks %>%
  knitr::kable(.)
```


```{r check-all-names}
these_sessions <- 1:dim(this_db_ss)[1]
all_checks_l <- lapply(these_sessions, check_session_name, this_db_ss, "NYU")

all_checks <- Reduce(function(x,y) merge(x,y, all=TRUE), all_checks_l)
all_checks %>%
  knitr::kable(.)
```

#### Release level

The Databrary release level is stored in the `session_release` variable.
The allowable release levels are \{SHARED, EXCERPTS, PUBLIC\}.
We may want to flag any PUBLIC releases, though.
For now, I'm going to include "PUBLIC" in the `ok_levels` parameter.

```{r}
release_level_ok <- function(i, df, ok_levels = c("SHARED", "EXCERPTS", "PUBLIC")) {
  this_release_level <- df$session_release[i]
  this_release_level %in% ok_levels
}

release_level_public <- function(i, df) {
  df$session_release[i] == "PUBLIC"
}

release_level_ok(12, this_db_ss)
release_level_public(12, this_db_ss)
```

#### Birthdate & testdate

The specification says birthdates should be after test dates and after 2018-12-15.
I've made the 'after' date a parameter.

```{r}
birthdate_not_NA <- function(i, df) {
  !is.na(df$participant.birthdate[i])
}

testdate_not_NA <- function(i, df) {
  !is.na(df$session_date[i])
}

birthdate_not_blank <- function(i, df) {
  df$participant.birthdate[i] != ""
}

testdate_not_blank <- function(i, df) {
  df$session_date[i] != ""
}

birthdate_is.Date <- function(i, df) {
  if (birthdate_not_NA(i, df) && birthdate_not_blank(i, df)) {
    lubridate::is.Date(lubridate::as_date(df$participant.birthdate[i]))
  } else {
    FALSE
  }
}

testdate_is.Date <- function(i, df) {
  if (testdate_not_NA(i, df) && testdate_not_blank(i, df)) {
    lubridate::is.Date(lubridate::as_date(df$session_date[i]))
  } else {
    FALSE
  }
}

birth_before_test <- function(i, df) {
  if (birthdate_is.Date(i,df) && testdate_is.Date(i,df)) {
    bdate <- lubridate::as_date(df$participant.birthdate[i])
    tdate <- lubridate::as_date(df$session_date[i])
    bdate < tdate    
  } else {
    NA    
  }
}

test_after_start <- function(i, df, start_date = "2018-12-15") {
  if (testdate_not_NA(i, df) && testdate_is.Date(i,df)) {
    tdate <- lubridate::as_date(df$session_date[i])
    start_date <- lubridate::as_date(start_date)
    tdate > start_date    
  } else {
    NA    
  }
}

birth_before_test(12, this_db_ss)
test_after_start(12, this_db_ss)
```

#### Age

The age reported in the Databrary spreadsheet is calculated from the birth and test dates.
The 12-month-old range is [11.75-12.25]; the 18-month-old range is [17.75-18.25]; the 24-month-old range is [23.75,24.25] months.

```{r}
age_in_mos <- function(i, df) {
  if (birthdate_is.Date(i,df) && testdate_is.Date(i,df)) {
    bdate <- lubridate::as_date(df$participant.birthdate[i])
    tdate <- lubridate::as_date(df$session_date[i])
    as.numeric(lubridate::as.duration(tdate - bdate), "months")    
  } else {
    NA
  }
}

age_in_mos(12, this_db_ss)
```


```{r}
age_valid <- function(age, min_age, max_age) {
  gte_min_age <- age >= min_age
  lte_max_age <- age <= max_age
  gte_min_age && lte_max_age && !is.na(age)
}

mos_12 <- function(age) {
  age_valid(age, 11.75, 12.25)
}

mos_18 <- function(age) {
  age_valid(age, 17.75, 18.25)
}

mos_24 <- function(age) {
  age_valid(age, 23.75, 24.25)
}

age_group_valid <- function(i, df) {
  this_age <- age_in_mos(i, df)
  mos_12(this_age) || mos_18(this_age) || mos_24(this_age)
}

mos_12(age_in_mos(12, this_db_ss))
mos_18(age_in_mos(12, this_db_ss))
mos_24(age_in_mos(12, this_db_ss))

age_group_valid(12, this_db_ss)
```

#### Gender

```{r}
gender_ok <- function(i, df) {
  df$participant.gender[i] %in% c("Male", "Female")
}

gender_ok(12, this_db_ss)
```

#### Race

```{r}
race_ok <- function(i, df) {
  race_categories <- c(
    "American Indian or Alaskan Native",
    "Asian",
    "Native Hawaiian or other Pacific Islander",
    "Black or African American",
    "White",
    "More than one",
    "Other",
    "Refused"
  )
  df$participant.race[i] %in% race_categories
}

race_ok(12, this_db_ss)
```

#### Ethnicity

```{r}
ethnicity_ok <- function(i, df) {
  ethnicity_categories <- c("Hispanic or Latino",
                            "Not Hispanic or Latino",
                            "Refused")
  
  df$participant.ethnicity[i] %in% ethnicity_categories
}

ethnicity_ok(12, this_db_ss)
```

#### Disability

```{r}
disability_ok <- function(i, df) {
  df$participant.disability[i] != "Typical"
}

disability_ok(12, this_db_ss)
```

#### Language

```{r}
language_ok <- function(i, df) {
  language_categories <- c("English",
                           "Spanish",
                           "English, Spanish",
                           "Spanish, English")
  
  df$participant.language[i] %in% language_categories
}

language_ok(12, this_db_ss)
```

### Assembling spreadsheet QA tests

```{r}
check_session_ss <- function(i, df, site_id) {
  out_df <- dplyr::tibble(
    session_name = df$session_name[i],
    name_has_PLAY = session_name_has_PLAY(i, df),
    name_has_site_id = session_name_has_site_id(i, df, site_id),
    name_has_sub_id = session_name_has_sub_id(i, df),
    name_has_corr_seps = session_name_has_correct_separators(i, df),
    name_play_id_valid = session_name_play_id_valid(i, df),
    name_length_ok = session_name_length_ok(i, df),
    release_level_ok = release_level_ok(i, df),
    release_level_public = release_level_public(i, df),
    birth_before_test = birth_before_test(i, df),
    test_after_start = test_after_start(i, df),
    age_group_valid = age_group_valid(i, df),
    gender_ok = gender_ok(i, df),
    race_ok = race_ok(i, df),
    ethnicity_ok = ethnicity_ok(i, df),
    disability_ok = disability_ok(i, df),
    language_ok = language_ok(i, df)
  )
  
  out_df
}

check_session_ss(1, this_db_ss, "NYU")
check_session_ss(2, this_db_ss, "NYU")
check_session_ss(3, this_db_ss, "NYU")
check_session_ss(4, this_db_ss, "NYU")
check_session_ss(5, this_db_ss, "NYU")
check_session_ss(6, this_db_ss, "NYU")
check_session_ss(7, this_db_ss, "NYU")
check_session_ss(8, this_db_ss, "NYU")
check_session_ss(9, this_db_ss, "NYU")
check_session_ss(10, this_db_ss, "NYU")
check_session_ss(11, this_db_ss, "NYU")
check_session_ss(12, this_db_ss, "NYU")
check_session_ss(13, this_db_ss, "NYU")
check_session_ss(14, this_db_ss, "NYU")
check_session_ss(15, this_db_ss, "NYU")
check_session_ss(16, this_db_ss, "NYU")
check_session_ss(17, this_db_ss, "NYU")
check_session_ss(18, this_db_ss, "NYU")
check_session_ss(19, this_db_ss, "NYU")
check_session_ss(20, this_db_ss, "NYU")
```

```{r}
these_sessions <- 1:dim(this_db_ss)[1]
for (i in these_sessions) {
  cat("session ", i, "\n")
  check_session_ss(i, this_db_ss, "NYU")
}

check_all_l <- lapply(these_sessions, check_session_ss, this_db_ss, "NYU")

check_all_df <- Reduce(function(x,y) merge(x,y, all=TRUE), check_all_l)
check_all_df %>%
knitr::kable(.)
```

