---
title: "site-report-template"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    keep_md: true
    theme: lumen
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: hide
params:
  vol_id: 881
  databrary_login: account@email.com
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install required packages
if (!require(tidyverse)) {
  install.packages("tidyverse")
}
if (!require(databraryapi)) {
  if (!require(devtools)) {
    install.packages("devtools")
  }
  devtools::install_github("PLAY-behaviorome/databraryapi")
}

library(tidyverse)

# Measure execution time

```

## Purpose

This document provides a template for how a site-specific progress report might be generated using the Databrary API and other sources.

## Set-up

### Log in to Databrary

Some of the functions require authentication to Databrary.
For this to work, you need to have entered your Databrary credentials into your own computer's credentials file.
On Mac OS, this is called Keychain.
If you have installed the `databraryapi` package, running `databraryapi::config_passwd()` will accept and store your credentials properly.

Once you have done that, you may render this file securely by executing the following code from the R console.
You will need to substitute your actual Databrary login ID for `myemail\@email.com`.

```
rmarkdown::render("site-report-template.Rmd", params = list(databrary_login = "myemail@email.com")
```

```{r}
if (databraryapi::login_db(params$databrary_login)) {
  message("Authenticated to Databrary")
} else {
  message("Authentication failure.")
}
```

### Get basic data about the volume

```{r}
vol_data <- databraryapi::list_volume_metadata(as.numeric(params$vol_id))

if (!is.null(vol_data)) {
  message(paste0("Progress report for volume ", as.character(vol_data$vol_id)))
  message(paste0("Volume name: ", vol_data$name))
  message(paste0("Investigators: ", vol_data$owners))
} else {
  message(paste0("Error in retrieving metadata from volume ", params$site_upload_vol_id))
}
```

Note, we can also put these variables in headers, like this:

### Volume `r vol_data$vol_id` : `r vol_data$name`

## Sessions created

If we have `read` privileges on the volume, we can see details about any sessions that have been created.

```{r}
these_sessions <- databraryapi::list_sessions(as.numeric(params$vol_id))
these_sessions %>%
  dplyr::arrange(desc(date)) %>%
  knitr::kable(.)
```

## Spreadsheet data

```{r}
this_volume <- databraryapi::download_containers_records(as.numeric(params$vol_id))

this_ss <- this_volume$records$measures

this_ss <- this_ss %>%
  filter(`1` != 1) # Weird, I know but filtering drops var names

this_ss %>%
  knitr::kable(.)
```

## Videos uploaded

```{r}
databraryapi::list_assets_by_type(as.numeric(params$vol_id))
```

## All files uploaded

```{r}
files <- databraryapi::list_assets_in_volume(as.numeric(params$vol_id))

files %>%
  knitr::kable(.)
```

