---
title: "api-explorations-kobotoolbox"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    keep_md: true
    theme: lumen
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: show
params:
  kobo_token: abcdefg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      out.width = "600px")

# Install packages
if (!require(tidyverse)) {
  install.packages("tidyverse")
}
if (!require(httr)) {
  install.packages("httr")
}

library(tidyverse) # so pipe %>% operator is available
```

## Purpose

This document explores the utility of using the KoBoToolbox.org API for file management of the PLAY Project survey data.

## Set-up

I used the KoBoToolbox.org support site, especially this page -- <http://support.kobotoolbox.org/en/articles/1559346-pulling-your-data-into-excel-power-query> -- for insights here.

1. I set up a new account on the server to test functionality.
2. I created a silly project called "Rick's Excellent Survey" with a small survey.
  - Here is the URL I sent to my lab's Discord: <https://ee.kobotoolbox.org/x/#jTDIfW5t>.

3. While logged in, I followed the instructions on this page

<http://support.kobotoolbox.org/en/articles/592398-api-and-rest-services>

to get my access token.
Specifically, I entered ` https://kf.kobotooltoolbox.org/token/?format=json` into a browser.

4. Then, I tested the token using this command in Terminal.app:

```
curl -X GET https://[kpi-url]/assets/?format=json -H "Authorization: Token [your_token_goes_here]"
```

Since I get a 200 success code, I am ready to do substantive things with the API.

## Accessing data

Following the instructions in

<http://support.kobotoolbox.org/en/articles/1559346-pulling-your-data-into-excel-power-query>,

I decided to try to get the data my lab group had entered into the test survey.

```{bash, eval = FALSE}
curl -X GET https://kc.kobotoolbox.org/api/v1/data.csv -H "Authorization: Token MY_TOKEN_HERE"
```

That command (with the appropriate token) returns a CSV with data about the surveys that have data for me.

Let's do this in R.

```{r}
r <- httr::GET(url = "https://kc.kobotoolbox.org/api/v1/data.csv", httr::add_headers("Authorization" = paste0("Token ", params$kobo_token)))
#status(r)
content(r, as = "parsed") %>%
  knitr::kable(.)
```

Note that to render this R Markdown document, I need to run the following command in the R console: `rmarkdown::render("api-explorations-kobotoolbox.Rmd", params=list(kobo_token="MY_TOKEN_HERE"))` substituting my actual token for `MY_TOKEN_HERE`.
The token is a string, so it needs to be surrounded by quotation marks, single or double.
This is messy, but it works, so we'll proceed.

### Getting specific individual-level responses

The prior set of commands gave us data about the survey data, but it didn't download the results.
Let's do that now.
First, I'm just going to copy and paste the `id` value for the file into the URL.
This should return JSON.

```{r}
r <- httr::GET(url = "https://kc.kobotoolbox.org/api/v1/data/341165", httr::add_headers("Authorization" = paste0("Token ", params$kobo_token)))
jsonlite::fromJSON(content(r, as = "text"))
```

So, that seems to work.
Let's clean it up a bit.
First, we'll save the output as a data frame so we can pull the survey ID as a parameter.

```{r}
surveys_r <- httr::GET(url = "https://kc.kobotoolbox.org/api/v1/data.csv", httr::add_headers("Authorization" = paste0("Token ", params$kobo_token)))
surveys_df <- content(surveys_r, as = "parsed")
```

Then, we'll use the `id` for the survey we want to build the next API call.

```{r}
silly_survey <- surveys_df %>%
  dplyr::filter(title == "Rick's Excellent Survey")

results_url <- paste0("https://kc.kobotoolbox.org/api/v1/data/", silly_survey$id)

data_r <- httr::GET(url = results_url, httr::add_headers("Authorization" = paste0("Token ", params$kobo_token)))

if (httr::status_code(data_r) == 200) {
  jsonlite::fromJSON(content(data_r, as = "text"))
} else {
  message(paste0("Status code: ", httr::status_code(data_r)))
}
```

Better, but let's see if grabbing a CSV reduces the post-download data-munging.

```{r}
results_url <- paste0("https://kc.kobotoolbox.org/api/v1/data/", silly_survey$id, ".csv")

data_r <- httr::GET(url = results_url, httr::add_headers("Authorization" = paste0("Token ", params$kobo_token)))

if (httr::status_code(data_r) == 200) {
  (responses_df <- readr::read_csv(content(data_r, as = "text")))
} else {
  message(paste0("Status code: ", httr::status_code(data_r)))
}
```

Ok, that's workable.
Let's extract the respondent's names.

```{r}
responses_df$What_is_your_name
```

This is going to work.

## Next steps

1. We should try extracting/exporting the PLAY survey data.
2. We could consider scripting/automating the generation of the PLAY surveys.
3. We'll need to think carefully about what post-download processing we need to do on the surveys.
