---
title: "PLAY workflow planning"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    keep_md: true
    theme: lumen
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      out.width = "600px")
```

# Purpose

To describe in detailed terms the steps involved in the PLAY workflow, especially focusing on file management and progress tracking.

<!-- Term/role definitions -->
```{r, child="workflow-1.0.Rmd"}
```

<!-- Term/role definitions -->
```{r, child="terminology.Rmd"}
```

# Background

The original source of many of these workflow ideas was this Google doc:

<https://docs.google.com/document/d/1t0vwlsN0rUdcNVjEx5VzEYa9KkLIdkxYh6cMrg3G-fU/edit>

The Google doc contains text from an unfunded NSF RIDIR proposal submitted in 2018 plus additional components added later.
At that time, we called the system we planned to use for PLAY a scientific process management (SPM) system with the working name `LabNanny`.

```{r, child="NSF-RIDIR-2018.Rmd"}
```

```{r, child="user-stories.Rmd"}
```
